\section{Project Management}
The project was managed using Jira~\cite{jira}, a widely adopted Agile project management tool. The development process followed an iterative approach, with tasks organized into epics that represent the major functional areas. Key epics included Technical Setup, Prototype Development, Feature Implementation, and Documentation.

The project was divided into several epics, each representing a major functional area or phase of development. Below is a detailed breakdown of the epics and their associated tasks:

\subsubsection{Epic 1: Technical Aspects}
This epic focused on setting up the foundational technical infrastructure for the project.
\begin{itemize}
    \item CB-4: Setup CI/CD with AKS
    \item CB-6: Setup API-Service Project
    \item CB-5: Setup Executor-Service Project
    \item CB-18: Setup Engine-Service Project
    \item CB-20: Add SqlServer Database to API Service
    \item CB-21: Setup Terraform Project
    \item CB-17: Maintain Kubernetes Manifests
    \item CB-22: Maintain CI/CD Pipeline
    \item CB-23: Maintain Terraform Infrastructure
    \item CB-38: Add MongoDB to Executor Service
\end{itemize}

\subsubsection{Epic 2: Prototype Development}
This epic involved creating the initial prototype and implementing core functionalities.
\begin{itemize}
    \item CB-8: Creating the First Prototype
    \item CB-9: Setup Jwt Authentication in the Api-Service
    \item CB-10: Develop Api Schema
    \item CB-11: Develop gRPC Schema between Api-Service \& Engine-Service
    \item CB-19: Implement Engine-Service Domain
    \item CB-24: Implement Engine-Service Application
    \item CB-13: Implement Api-Service Logic
    \item CB-25: Merge Engine into API Temporarily
\end{itemize}

\subsubsection{Epic 3: Adding Core Features}
This epic focused on adding essential features to the platform.
\begin{itemize}
    \item CB-26: Adding Essential Features
    \item CB-27: Implement User Images Endpoints
    \item CB-29: Add More User Fields
    \item CB-28: Maintain Api Endpoints
    \item CB-30: Add ApiAction Node
    \item CB-12: Develop gRPC Schema between Engine-Service \& Executor-Service
    \item CB-32: Add Generation \& SmartSwitch Nodes
    \item CB-14: Implement Executor-Service Logic
    \item CB-33: Add Image Ports for Interaction Node
\end{itemize}

\subsubsection{Epic 4: Adding Advanced Features}
This epic involved implementing additional advanced features to enhance the platform's capabilities.
\begin{itemize}
    \item CB-35: Adding Extra Features
    \item CB-37: Add ImageData to InteractionOptionMetas
    \item CB-36: Add Avatar Picture to Chatbots
    \item CB-41: Return ProfilePicture with User details
    \item CB-42: Add Object Visual fields
    \item CB-43: Add Chatbot-Graph Query for Owners
    \item CB-31: Add Entities Statistics
\end{itemize}

\subsubsection{Epic 5: Domain Aspects}
This epic focused on project documentation, reporting, and final deliverables.
\begin{itemize}
    \item CB-7: Maintain Pages \& ReadMes
    \item CB-15: Add Workflow Examples
    \item CB-16: Write Project Report
    \item CB-39: Create Demo \& Presentation
\end{itemize}